What does the crowd believe? A hierarchical approach to estimating subjective beliefs from empirical data

### 2016-02-01 text/01_CogSci_abstract/paper.tex
CogSci abstract final edits

\usepackage{cogsci}
\usepackage{pslatex}
\usepackage{apacite}
\usepackage{subcaption}
\usepackage{todonotes}
\usepackage{amsmath}
\usepackage{color}
\usepackage{booktabs}

@@

\author{{\large \bf Michael Franke} \\
  michael.franke@uni-tuebingen.de \\
  Department of Linguistics, Wilhelmstra\ss e 19 \\
 72074 T\"{u}bingen, Germany \AND 
 {\large \bf Erin Bennett, Judith Degen, Michael Henry Tessler, Noah D. Goodman}\\
     \{ebennett, jdegen, mtessler, ngoodman\}@stanford.edu \\
     Department of Psychology, Stanford University \\
     450 Serra Mall, Stanford, CA 94305 USA }

@@

\begin{abstract}
  Experimental participants' beliefs about everyday events are both of theoretical interest in their own right and an important ingredient in model building---especially in cognitive Bayesian models of
  phenomena such as logical reasoning, future predictions, and language use. Here, we explore
  several recently used methods for measuring subjective beliefs about unidimensional
  contiguous properties, such as the likely price of a new watch. We use a hierarchical
  Bayesian model for inferring likely population-level beliefs as the central tendency of
  participants' individual-level beliefs.  Three different dependent measures are related to
  individual-level beliefs through likelihood linking functions: (i) judgements of
  (relative) likelihood of intervals of values via continuous sliders, (ii) a give-a-number
  task, and (iii) choice of the more likely of two intervals of values. Our results suggest
  that using averaged normalized slider ratings for binned quantities is a practical and fairly
  good approximator of inferred population-level beliefs.

@@

We cannot look into a person's head. But in making sense of observed behavior we readily
ascribe beliefs and desires to fellow agents. This happens intuitively, in folk psychology, but
also in science. Scientific ascription of latent mental states plays an important role in many
explanations of higher-order cognition: decision making, planning, reasoning, and language
use. It is therefore vital to have methods for validating explanatory mental state
ascriptions.

A family of models where this is particularly pressing are Bayesian models of cognition which
seek to explain task behavior in a variety of domains as partially informed by what
participants believe about mundane events---their \emph{prior beliefs}. Take interpretation of
language. Empirical data on whether a statement like ``That watch cost $n$ dollars'' is
understood to convey speaker affect, rather than literal meaning, can be explained well by a
Bayesian model of utterance interpretation \citep{KaoWu2014:Nonliteral-Unde}. In this model a
crucial role is played by an empirical measure of participants' expectations about the likely
or normal price of a watch.  Other examples of domains in which empirically successful models
have included a measure of participants' prior beliefs include making predictions about
everyday events \citep{GriffithsTenenbaum2006:Optimal-Predict}, referential communication
\citep{FrankGoodman2012:Predicting-Prag}, the strength of pragmatic enrichments
\citep{DegenTessler2015:Wonky-worlds:-L}, or the interpretation of vague quantifiers
\citep{SchollerFranke2015:Semantic-values}. \mf{anyone wants any other references here?}

Many methods of assessing subjective beliefs exist. One approach is to take actual frequencies
as an approximation to subjective beliefs
\citep{GriffithsTenenbaum2006:Optimal-Predict}. Unfortunately, the relevant data may not be
available (e.g., for one-shot or imaginary events) and real-world frequencies may deviate from
participants' subjective beliefs for many reasons.

Another possibility is to empirically measure subjective beliefs by \emph{give-a-number}
tasks. The simplest version would be this: being told that John just bought a new watch,
participants are asked for a single numerical estimate of its price. This task is easy to
comprehend and implement, but a single number does not provide much information about the
subjective belief that it is a manifestation of. One solution is to infer which
parameterized distribution best explains the observed number choices, either at the individual
level \citep{Manski2004:Measuring-Expec} or on the population level
\citep{TauberSteyvers2013:Inferring-Subje}.

More sophisticated \emph{give-a-number} tasks give more information, but can be rather complex
and more difficult to implement. A prominent method in economics uses \emph{scoring rules}
\citep{Savage1971:Elicitation-of-,AndersenFountain2014:Estimating-Subj,SchlagTremewan2014:A-penny-for-you}. Roughly
put, scoring rules are schemes of rewarding participants' answers that make sure that responses
(by rational participants) faithfully reflect a measure of interest: the actual subjective
probability of an event, the mean of a distribution, a credible interval etc. Scoring-rule
tasks require participants to become sufficiently familiar with the (usually probabilistic)
payoff scheme. Another insightful, but also complex approach is to use a cleverly designed
\emph{iterated learning paradigm} \citep{LewandowskyGriffiths2009:The-Wisdom-of-I}.

\begin{table*}
  \footnotesize
  \centering
  \begin{tabular}{l p{2.2cm} p{2.5cm} p{3.5cm} p{3cm} p{2.5cm}}
	\toprule
	\textbf{Item} & \textbf{Bins} (\{min, max\} step; units)& \textbf{Context sentence} & \textbf{GAN question} & \textbf{BH frame} & \textbf{PC frame} \\
	\midrule
    coffee &  \{$<$44, $>$200\} 2; degrees  & X has just fetched himself a cup of coffee from the office vending machine. & What do you think the temperature of his coffee is?  & His coffee was the following temperatures & The temperature of his coffee is N degrees.\\
    	\midrule
	commute &  \{0, $>$98\} 7; minutes & X commuted to work yesterday. & How many minutes do you think she spent commuting yesterday? & She commuted for the following numbers of minutes yesterday & She spent N minutes commuting.\\
		\midrule
	joke &  \{0, 14\} 1; children  & X told a joke to 14 kids. & How many of the kids do you think laughed? & the following number of kids laughed & N of the children laughed.\\
    	\midrule
	laptop &  \{0, $>$7500\} 500; dollars& X bought a laptop. & How much do you think it cost? & The laptop cost the following numbers of dollars & The laptop cost \$N.\\
	\midrule
    marbles &  \{0, 14\} 1; marbles & X threw 14 marbles into a pool. & How many of the marbles do you think sank? & The following number of marbles sank & N of the marbles sank.\\
	\midrule
	movies &  \{0, $>210$\} 16; minutes& X just went to the movies to see a blockbuster. & How many minutes long do you think the movie was? & The movie was the following numbers of minutes long & The movie was N minutes long.\\
	\midrule
	TV &  \{0, $>$43\} 3; hours & X watched TV last week. & How many hours do you think he spent watching TV last week? & He watched TV for the following numbers of hours last week & He spent N hours watching TV.\\
	\midrule
	watch &  \{0, $>$750\} 50; dollars& X bought a watch.& How much do you think it cost? & It cost the following numbers of dollars & The watch cost \$N.\\
    \bottomrule
  \end{tabular}
  \caption{Experimental items. \emph{X} was a randomly generated name (different on each trial). \emph{N} was one of the bins.}
  \label{tab:Items}
\end{table*}

In sum, there is tradeoff between simplicity of paradigms and their information content. Ideally, we
would like to have an experimental method for measuring subjective beliefs that (i) provides
sufficient and reliable-enough information about subjective beliefs to derive testable
predictions from cognitive models that rely on such information, (ii) is easy to understand by
 participants, (iii) is easy to implement by researchers whose focus and expertise is not
belief-elicitation as such, and that (iv) does not rely on sophisticated methods of extracting
the relevant information from the observed data. Moreover, the ideal method would be (v)
flexible enough to allow inferred subjective belief distributions beyond standard parameterized
distributions and (vi) would provide us with a reasonable approximation of a population-level
belief, i.e., an estimate of the central tendency or average of subjective beliefs in a given
population. The latter would warrant using one set of participants for measuring prior beliefs and
another for whatever other task is of interest.

A simple technique that seems to fit this bill is the \emph{binned histogram} task that has
recently been used with apparent success
\citep{KaoWu2014:Nonliteral-Unde,SchollerFranke2015:Semantic-values}. \mf{someone please add
  references: where did you use binned sliders?} \mht{I used ``categorical'' sliders for discrete priors in my syllogistic reasoning / belief bias stuff; and so did justine in her metaphor work...}Participants adjust sliders in order to
express their (relative) subjective beliefs about how likely it is that the value of an
uncertain contiguous quantity lies in some interval of possible values (a bin). E.g.,
participants read that John bought a watch.  To report their beliefs about the watch's price,
they adjust sliders whose endpoints are labelled as ``extremely likely'' and ``extremely
unlikely.'' Each slider corresponds to one out of 15 bins that partition the range of plausible
values (established by a pre-test). E.g., for the price of a watch bins could be ``\$0-\$50'',
``\$50-\$100'', etc. up to ``\$700-\$750'' and ``more than \$750''. Each participant's slider
ratings are normalized within each item, and the results are averaged across participants to obtain
an estimate of the population's average belief about each item. These averaged normalized
slider ratings per bin (henceforth: mean slider ratings) look intuitively plausible and yield
good results if fed into cognitive models that predict behavior in language or reasoning tasks,
for instance.

Explanatory success notwithstanding, the question remains whether mean slider ratings measure
what we would like them to. Are these good approximations of a central tendency of participants'
individual beliefs? Are these measures consistent with participants' behavior in other tasks, such
as \emph{give-a-number}, as well? To address this issue we collected data in a within-subject paradigm 
from three task types: (i) \emph{binned histograms}, (ii) \emph{give-a-number} and (iii)
\emph{paired comparisons}, i.e., a direct comparison of two bins from the \emph{binned
  histograms} task. Using a Bayesian hierarchical model, we used the data from all three
dependent measures to infer likely latent subjective beliefs, where each subjective belief is,
intuitively, a noisy perturbation of a population-level belief. We find that mean \emph{a
  posteriori} population-level beliefs are approximated well by mean slider ratings, suggesting
that the latter may indeed be a plausible, yet cheap measure of what the crowd believes.
Moreover, the model is able to capture participants' behavior in all three task types reasonably
well, suggesting that what mean slider ratings measure is what we think it is: a population-level
central tendency of latent subjective beliefs.

@@

\subsection{Methods}

\paragraph{Participants, procedure and materials} We recruited 20 self-reported English native speakers  over Mechanical Turk.

We elicited prior beliefs for eight different items (listed in
\tableref{tab:Items}) using three different dependent measures: \emph{binned histograms},
\emph{give-a-number} and \emph{paired comparisons}. Each participant rated each item using each
dependent measure. Trial order was randomized.

On \emph{give-a-number} (GAN) trials, participants saw the context sentence and GAN question
for each item (see \tableref{tab:Items}) and were asked to provide one number by adjusting a
slider with endpoints labeled as the lowest and highest number for that item. Min and max
numbers are shown in \tableref{tab:Items} and were taken from previous studies that had used
these items
\cite{DegenTessler2015:Wonky-worlds:-L,SchollerFranke2015:Semantic-values,KaoWu2014:Nonliteral-Unde}. The
selected number appeared above the slider so participants knew exactly what the value of the
slider would be.

@@

\figref{fig:Results} shows mean slider ratings alongside the frequencies of number choices in the \emph{give-a-number} task. It looks like the
latter could be samples from the former, with a tendency to modal choices. But, despite the use
of sliders, some \emph{give-a-number} results still seem to reflect a tendency towards round or
salient numbers. E.g., in item \emph{coffee} more than 40\% of participants guessed that a
coffee from the vending machine was ca. 150 degrees Fahrenheit (bin 10). The results from the
\emph{paired comparison} seem consistent with the mean slider ratings as well, albeit not as
straightforwardly as one might think. This is clearest from the \emph{marbles} case. While the
mean slider ratings indicate that bins 2, 6 and 11 were all felt to be equally likely on
average, almost every participant chose the higher bin in direct bin comparisons 2 vs 6 and 6
vs 11. A potential explanation for this, which we will implement formally in the
data-generating model, is that the \emph{paired comparison} condition invited participants to think
about what they thought was mostly likely the case (usually: bin 15 in the
\emph{marbles} case) and to choose the bin that is closest to that.

\begin{figure}[t!]
  \centering
  \begin{subfigure}{0.5\textwidth}
    \includegraphics[width = \textwidth]{plots/data_sliderNumber.pdf}
    \caption{Red: proportion of choosing a number in each bin on \emph{give-a-number} trials. Black: mean slider ratings on \emph{binned histogram} trials.}
    \label{fig:slider}
  \end{subfigure}

  \begin{subfigure}{0.5\textwidth}
    \includegraphics[width = \textwidth]{plots/data_choice.pdf}
    \caption{Proportion of choosing the higher bin on \emph{paired comparison} trials.}
    \label{fig:lighting}
  \end{subfigure}

  \caption{Experimental results. Error bars show bootstrapped 95\% confidence intervals.}
  \label{fig:Results}
\end{figure}

@@

All three pieces of data are to be explained as functions of subjective beliefs $P_{ij}$, with
$P_{ijk}$ being participant $i$'s belief about the relative likelihood of bin $k$ for item
$j$. Each $P_{ij}$ defines a likelihood for our data, via appropriate link functions (to be
spelled out presently). Variance in subjective beliefs is harnessed by a population-level
hyper-prior with central tendency $Q_{j}$, i.e., a stochastic vector of length 15. The
structure of this model is pictured in \figref{fig:ModelGraph}.

To fill the structure in \figref{fig:ModelGraph} with life, we need to spell out three
parameterized link functions, one for each task type, and the relation between population-level
belief $Q_j$ to individual beliefs $P_{ij}$. Let's start with the latter. For fixed $Q_j$, the
idea is that $P_{ij}$ are noise-perturbed variants scattered around $Q_j$, with some parameter
$w$ to determine how much perturbation we should expect.
 To realize this, the model assumes
that $P_{ij}$ are distributed according to a Dirichlet distribution with weights given by
$w Q_{j}$:
\begin{align*}
  Q_j & \sim \text{Dirichlet}(1, \dots, 1) & w & \sim \text{Gamma}(2,0.1) \\
  P_{ij} & \sim \text{Dirichlet}( w Q_j)
\end{align*}
The higher $w$, the more likely it is that $P_{ij}$ is ``close'' to $Q_j$.

@@

Finally, consider the link function for \textbf{bin comparisons}. We are interested in the likelihood
with which participant $i$ selects the higher bin for item $j$ in bin comparison condition
$l$. Suppose $l$ is about comparing the lower bin $b_l$ to the higher $b_h$. The perhaps most
natural approach would be to link the likelihood of choosing $b_h$ over $b_l$ to the difference
between $P_{ijb_h}$ and $P_{ijb_l}$. However, as discussed above, this does not appear to be
what participants were doing. Indeed, a model that implements this idea blatantly failed to capture the
relevant regularities in the data. Another plausible link function is to assume that
what matters in bin comparisons is the distance to the mode of $P_{ij}$: soft-max prefer the
bin that is closer to the mode of $P_{ij}$; select randomly if both bins are equally far from
the prototype.\footnote{Notice that
  $(1 + \exp(2b(1-p^{\text{high}}_{ijl})) )^{-1} = \frac{\exp(b p^{\text{high}})}{\exp(b
    p^{\text{high}}) + \exp(b p^{\text{low}})}$
  with $p^\text{low}_{ijl} = 2 - p^\text{high}_{ijl}$.
  \mht{I am unable to notice this. Double check? Intuition tells me $p^\text{low}_{ijl} = 1 - p^\text{high}_{ijl}$.}
  }
\begin{align*}
  c_{ijl} & \sim \text{Bern}( (1 + \exp(2b(1-p^{\text{high}}_{ijl})) )^{-1} ) \ \ \ 
  b  \sim \text{Gamma}(2,1) \\
  p^\text{high}_{ijl} & = \begin{cases}
    2 & \text{if $mode(P_{ij})$ is closer to higher} \\
    & \text{ bin of $l$ than to lower bin } \\ 1 & \text{if equal
      distance} \\ 0 & \text{otherwise}  
  \end{cases}
\end{align*}

\begin{figure}[]
  \centering
  \includegraphics[width = 0.4\textwidth]{modelGraph/modelGraphNoMath.pdf}
  \caption{The data-generating model as a probabilistic graphical model, following conventions
    of \citet{LeeWagenmakers2013:Bayesian-Cognit}. Shaded nodes are observed, white nodes are
    latent variables. Square nodes represent categorical, round nodes continuous
    variables. Boxes indicate scope of indices.}
  \label{fig:ModelGraph}
\end{figure}

@@

Means and bounds of 95\% HDIs of the posteriors for model parameters are in
Table~\ref{tab:SummaryStats}. Posterior credible levels of $w$ allow for a limited amount of
slack around $Q_j$. Values for $\kappa$ indicate that, on average, participants may not have had a
preference for or against extreme slider ratings. Relatively high values of $a$ indicate that
participants, on average, had a strong tendency to choose their mode in the \emph{give-a-number}
task.
\begin{table}[ht]
\centering
\begin{tabular}{rlllll}
 & $w$ & $\kappa$ & $\sigma$ & $a$ & $b$ \\ \hline
  lower & 14.65 &  0.98 &  0.26 & 22.04 &  1.11 \\ 
  mean & 15.55 &  0.99 &  0.28 & 27.43 &  1.27 \\ 
  upper & 16.48 &  0.99 &  0.31 & 32.95 &  1.42 \\ 
   \hline
\end{tabular}
\caption{Summary statistics for posterior on parameters}
\label{tab:SummaryStats}
\end{table}

Of most theoretical interest are posterior estimates of $Q_j$. \figref{fig:PosteriorQj}
shows means of the posterior $Q_j$, with their 95\% HDIs, alongside the averaged normalized
slider ratings. The latter provide a very good approximation of the latent, inferred
population-level beliefs. Inspection of posteriors of individual $P_{ij}$ shows that there is
ample variation between participants. Nonetheless, the way the model suggests we should think about
harnessing the individual $P_{ij}$s under a population-level central tendency is closely
approximated by simply averaging over slider ratings. Although the match is clearly not
perfect, it is good enough to maintain that the latter are a reasonable (enough) and practical
way of assessing what the crowd believes despite individual differences.

\begin{figure}
  \centering
  \includegraphics[width = 0.5\textwidth]{plots/pop_priors.pdf}
  \caption{Means of posteriors over $Q_j$ in black with gray area indicating 95\% HDIs. Red
    lines give the average normalized slider ratings for comparison.}
  \label{fig:PosteriorQj}
\end{figure}

@@

MF's work was supported by the Institutional Strategy of the University of T̈\"{u}bingen (Deutsche
Forschungsgemeinschaft, ZUK 63). MF and JD's work was supported by the Priority Program XPrag.de (DFG Schwerpunktprogramm
1727). This work was further supported by ONR grant N00014-13-1-0788 and a James S. McDonnell Foundation Scholar Award to NDG and an SNF Early Postdoc.Mobility Award to JD.

>>>>

\usepackage{cogsci}
\usepackage{pslatex}
\usepackage{apacite}
\usepackage{subcaption}
\usepackage{todonotes}
\usepackage{amsmath}
\usepackage{color}
\usepackage{booktabs}
\usepackage{caption}
\captionsetup{belowskip=0pt,aboveskip=2pt}
\setlength{\textfloatsep}{9pt}

@@

\author{{\large \bf Michael Franke, Fabian Dablander, Anthea Sch\"{o}ller} \\
  \{michael.franke, fabian.dablander, anthea.schoeller\}@uni-tuebingen.de \\
  Department of Linguistics, Wilhelmstra\ss e 19 \\
  72074 T\"{u}bingen, Germany \AND
  {\large \bf Erin Bennett, Judith Degen, Michael Henry Tessler, Justine Kao, Ciyang Qing, Noah D. Goodman}\\
  \{ebennett, jdegen, mtessler, justinek, qciyang, ngoodman\}@stanford.edu \\
  Department of Psychology, Stanford University \\
  450 Serra Mall, Stanford, CA 94305 USA }

@@

\begin{abstract}
  Experimental participants' beliefs about everyday events are both of theoretical interest in
  their own right and an important ingredient in model building---especially in cognitive
  Bayesian models of phenomena such as logical reasoning, future predictions, and language
  use. Here, we explore several recently used methods for measuring subjective beliefs about
  unidimensional contiguous properties, such as the likely price of a new watch. We use a
  hierarchical Bayesian model for inferring likely population-level beliefs as the central
  tendency of participants' individual-level beliefs.  Three different dependent measures are
  used to infer latent beliefs: (i) slider ratings of (relative) likelihood of intervals of
  values, (ii) a give-a-number task, and (iii) choice of the more likely of two intervals of
  values. Our results suggest that using averaged normalized slider ratings for binned
  quantities is a practical and fairly good approximator of inferred population-level beliefs.

@@

We cannot look into a person's head. But in making sense of observed behavior we readily
ascribe beliefs and desires to fellow agents. This happens intuitively, in folk psychology, but
also in science. Scientific ascription of latent mental states plays an important role in many
explanations of higher-order cognition: decision making, reasoning, language use etc. It is
therefore vital to have methods for validating explanatory mental state ascriptions.

A family of models where this is particularly pressing are Bayesian models of cognition which
seek to explain task behavior in a variety of domains as partially informed by what
participants believe about mundane events---their \emph{prior beliefs}. Take interpretation of
language. Empirical data on whether a statement like ``That watch cost $n$ dollars'' is
understood to convey speaker affect, rather than literal meaning, can be explained well by a
Bayesian model of utterance interpretation \citep{KaoWu2014:Nonliteral-Unde}. This model
assigns a crucial role to an empirical measure of participants' expectations about the likely
or normal price of a watch.  Other examples of domains in which empirically successful models
have included a measure of participants' prior beliefs include making predictions about
everyday events \citep{GriffithsTenenbaum2006:Optimal-Predict}, referential communication
\citep{FrankGoodman2012:Predicting-Prag}, the strength of pragmatic enrichments
\citep{DegenTessler2015:Wonky-worlds:-L}, or the interpretation of quantifiers
\citep{SchollerFranke2015:Semantic-values}.

One method of getting at subjective beliefs is to take actual frequencies as an approximation
to subjective beliefs \cite<e.g.>{GriffithsTenenbaum2006:Optimal-Predict}. Unfortunately,
frequency data may be unavailable (e.g., one-shot events) or deviate from participants'
subjective beliefs in crucial respects.

Another frequent approach is to empirically measure subjective beliefs by \emph{give-a-number}
tasks. The simplest version would be this: being told that John just bought a new watch,
participants are asked for a single numerical estimate of its price. This task is easy to
comprehend and implement, but a single number does not provide much information about the
subjective belief that it is a manifestation of. One solution is to infer which parameterized
distribution best explains the observed number choices, either at the individual level
\citep{Manski2004:Measuring-Expec} or at the population level
\citep{TauberSteyvers2013:Inferring-Subje}.

More sophisticated \emph{give-a-number} tasks give more information, but can be difficult to
implement and analyze. A prominent method in economics uses \emph{scoring rules}
\citep{Savage1971:Elicitation-of-,AndersenFountain2014:Estimating-Subj,SchlagTremewan2014:A-penny-for-you}. Roughly
put, scoring rules are schemes of rewarding participants' answers that make sure that responses
(by rational participants) faithfully reflect a measure of interest: the actual subjective
probability of an event, the mean of a distribution, a credible interval etc. Scoring-rule
tasks require participants to become sufficiently familiar with the (usually probabilistic)
payoff scheme. Another insightful, but also complex approach is to use a cleverly designed
\emph{iterated learning paradigm} \citep{LewandowskyGriffiths2009:The-Wisdom-of-I}.

\begin{table*}
  \footnotesize
  \centering
  \begin{tabular}{l p{2.2cm} p{2.5cm} p{3.5cm} p{3cm} p{2.5cm}}
	\toprule
	\textbf{Item} & \textbf{Bins} (\{min, max\} step; units)& \textbf{Context sentence} & \textbf{GAN question} & \textbf{BH frame} & \textbf{PC frame} \\
	\midrule
    coffee &  \{$<$44, $>$200\} 2; degrees  & X has just fetched himself a cup of coffee from the office vending machine. & What do you think the temperature of his coffee is?  & His coffee was the following temperatures & The temperature of his coffee is N degrees.\\
    	\midrule
	commute &  \{0, $>$98\} 7; minutes & X commuted to work yesterday. & How many minutes do you think she spent commuting yesterday? & She commuted for the following numbers of minutes yesterday & She spent N minutes commuting.\\
		\midrule
	joke &  \{0, 14\} 1; children  & X told a joke to 14 kids. & How many of the kids do you think laughed? & The following number of kids laughed & N of the children laughed.\\
    	\midrule
	laptop &  \{0, $>$7500\} 500; dollars& X bought a laptop. & How much do you think it cost? & The laptop cost the following numbers of dollars & The laptop cost \$N.\\
	\midrule
    marbles &  \{0, 14\} 1; marbles & X threw 14 marbles into a pool. & How many of the marbles do you think sank? & The following number of marbles sank & N of the marbles sank.\\
	\midrule
	movies &  \{0, $>210$\} 16; minutes& X just went to the movies to see a blockbuster. & How many minutes long do you think the movie was? & The movie was the following numbers of minutes long & The movie was N minutes long.\\
	\midrule
	TV &  \{0, $>$43\} 3; hours & X watched TV last week. & How many hours do you think he spent watching TV last week? & He watched TV for the following numbers of hours last week & He spent N hours watching TV.\\
	\midrule
	watch &  \{0, $>$750\} 50; dollars& X bought a watch.& How much do you think it cost? & It cost the following numbers of dollars & The watch cost \$N.\\
    \bottomrule
  \end{tabular}
  \caption{Experimental items. \emph{X} was a randomly generated name (different on each trial). \emph{N} was one of the bins.}
  \label{tab:Items}
\end{table*}

In sum, there is tradeoff between simplicity of paradigms and their information
content. Ideally, we would like to have an experimental method for measuring subjective beliefs
that (i) provides sufficient and reliable-enough information about subjective beliefs to derive
testable predictions from cognitive models that rely on such information, (ii) is easy to
understand by participants, (iii) is easy to implement, and that (iv) does not require
sophisticated means of data analysis. Moreover, the ideal method would be (v) flexible enough
to allow inferred subjective belief distributions beyond standard parameterized distributions
and (vi) would provide a good approximation of the central tendency or average of subjective
beliefs in a given population. The latter would allow using one set of participants for
measuring prior beliefs and another for whatever other task is of interest, so as to avoid
potential cross-over effects.

A simple technique that seems to fit this bill is the \emph{binned histogram} task that has
recently been used with apparent success
\cite<e.g.>{KaoWu2014:Nonliteral-Unde,KaoBergen2014:Formalizing--th,Tessler2015:Understanding-B,SchollerFranke2015:Semantic-values}. Participants
adjust sliders to express (relative) subjective beliefs about how likely the value of an
uncertain contiguous quantity lies in some interval of possible values (a bin). E.g., to report
beliefs about the a watch's price, participants adjust sliders whose endpoints are labelled
``extremely likely'' and ``impossible.'' Each slider corresponds to one of 15 bins that
partition the range of plausible values (established by a pre-test), such as ``\$0-\$50'',
``\$50-\$100'', etc. up to ``\$700-\$750'' and ``more than \$750.'' Each participant's slider
ratings are normalized and the results averaged across participants. The resulting \emph{mean
  slider ratings} look like plausible population-level beliefs and give good results when fed
into cognitive models that predict task behavior based on prior expectations.

Explanatory success aside, the question remains whether mean slider ratings measure
what we would like them to. Are these good approximations of a central tendency of participants'
individual beliefs? Are these measures consistent with participants' behavior in other tasks, such
as \emph{give-a-number}, as well? To address this issue we collected data in a within-subject paradigm 
from three task types: (i) \emph{binned histograms}, (ii) \emph{give-a-number} and (iii)
\emph{paired comparisons}, i.e., a direct comparison of two bins from the \emph{binned
  histograms} task. Using a Bayesian hierarchical model, we used the data from all three
dependent measures to infer likely latent subjective beliefs, where each subjective belief is,
intuitively, a noisy perturbation of a population-level belief. We find that mean \emph{a
  posteriori} population-level beliefs are approximated well by mean slider ratings, suggesting
that the latter may indeed be a plausible, yet cheap measure of what the crowd believes.
Moreover, the model is able to capture participants' behavior in all three task types reasonably
well, suggesting that what mean slider ratings measure is what we think it is: a population-level
central tendency of latent subjective beliefs.

@@

\paragraph{Participants, procedure and materials} We recruited 20 self-reported English native
speakers over Mechanical Turk and collected responses for eight different items (listed in
\tableref{tab:Items}) using three different dependent measures: \emph{binned histograms},
\emph{give-a-number} and \emph{paired comparisons}. Each participant rated each item using each
dependent measure. Trial order was randomized.

On \emph{give-a-number} (GAN) trials, participants saw the context sentence and GAN question
for each item (see \tableref{tab:Items}) and provided one number by adjusting a
slider with endpoints labeled as the lowest and highest number for that item. Min and max
numbers are shown in \tableref{tab:Items} and were taken from previous studies that had used
these items
\cite{DegenTessler2015:Wonky-worlds:-L,SchollerFranke2015:Semantic-values,KaoWu2014:Nonliteral-Unde}. The
selected number appeared above the slider so participants knew exactly what the value of the
slider would be.

@@

\paragraph{Results} \figref{fig:Results} shows mean slider ratings alongside the frequencies of
number choices in the \emph{give-a-number} task. It looks like the latter could be samples from
the former, with a tendency to modal choices. But some \emph{give-a-number} results seem
influenced by a tendency towards round or salient numbers. E.g., in item \emph{coffee} more
than 40\% of participants guessed that a coffee from the vending machine was ca.~150$^{\circ}$F
(bin 10). The results from the \emph{paired comparison} seem consistent with the mean slider
ratings as well, albeit not as straightforwardly as one might think. This is clearest from the
\emph{marbles} case. While the mean slider ratings suggest that bins 2, 6 and 11 were
considered roughly equiprobable on average, almost every participant chose the higher bin in
direct bin comparisons 2 vs 6 and 6 vs 11. A potential explanation for this, which we will
implement formally in the data-generating model, is that the \emph{paired comparison} condition
invited participants to think about what they thought was mostly likely the case (usually: bin
15 in the \emph{marbles} case) and to choose the bin that is closest to that.

\begin{figure}[t!]
  \centering
  \begin{subfigure}{0.475\textwidth}
    \includegraphics[width = \textwidth]{plots/data_sliderNumber.pdf}
    \caption{Red: proportion of bins corresponding to number choices on \emph{give-a-number} trials. Black: mean slider ratings on \emph{binned histogram} trials.}
    \label{fig:slider}
  \end{subfigure}

  \begin{subfigure}{0.475\textwidth}
    \includegraphics[width = \textwidth]{plots/data_choice.pdf}
    \caption{Proportion of higher bin choices on \emph{paired comparison} trials.}
    \label{fig:lighting}
  \end{subfigure}

  \caption{Average data. Bars are bootstrapped 95\% CIs.}
  \label{fig:Results}
\end{figure}

@@

All three pieces of data are to be explained as functions of subjective beliefs $P_{ij}$, with
$P_{ijk}$ being participant $i$'s belief about the relative likelihood of bin $k$ for item
$j$. Each $P_{ij}$ defines a likelihood for our data, via appropriate link functions. Variance
in subjective beliefs is harnessed by a population-level hyper-prior with central tendency
$Q_{j}$. The structure of this model is pictured in \figref{fig:ModelGraph}.

To fill the structure in \figref{fig:ModelGraph} with life, we need to spell out three
parameterized link functions, one for each task type, and the relation between population-level
belief $Q_j$ and individual beliefs $P_{ij}$. Let's start with the latter. The idea is that
$P_{ij}$ are noise-perturbed variants scattered around $Q_j$, with some parameter $w$ to
determine how much perturbation we should expect.  To realize this, the model assumes that
$P_{ij}$ are distributed according to a Dirichlet distribution with weights given by $w Q_{j}$:
\begin{align*}
  Q_j & \sim \text{Dirichlet}(1, \dots, 1) & w & \sim \text{Gamma}(2,0.1) \\
  P_{ij} & \sim \text{Dirichlet}( w Q_j)
\end{align*}
The higher $w$, the more likely it is that $P_{ij}$ is ``close'' to $Q_j$.

@@

Finally, consider the link function for \textbf{bin comparisons}. We are interested in the
likelihood with which participant $i$ selects the higher bin for item $j$ in bin comparison
condition $l$. Suppose $l$ is about comparing the lower bin $b_l$ to the higher $b_h$. The
perhaps most natural approach would be to link the likelihood of choosing $b_h$ over $b_l$ to
the difference between $P_{ijb_h}$ and $P_{ijb_l}$. However, as discussed above, this does not
appear to be what participants were doing. Indeed, a model that implements this idea blatantly
fails to capture the relevant regularities in the data. Another plausible link function is to
assume that what matters is the distance to the mode of $P_{ij}$: soft-max prefer the bin that
is closer to the mode of $P_{ij}$; select randomly if both bins are equally far from the
prototype.\footnote{$(1 + \exp(2b(1-x)) )^{-1} = \frac{\exp(b x)}{\exp(b
    x) + \exp(b y)}$
  if $x = 2 - y$.}
\begin{align*}
  c_{ijl} & \sim \text{Bern}( (1 + \exp(2b(1-p^{\text{high}}_{ijl})) )^{-1} ) \ \ \ 
  b  \sim \text{Gamma}(2,1) \\
  p^\text{high}_{ijl} & = \begin{cases}
    2 & \text{if $mode(P_{ij})$ is closer to higher} \\
    & \text{ bin of $l$ than to lower bin } \\ 1 & \text{if equal
      distance} \\ 0 & \text{otherwise}  
  \end{cases}
\end{align*}

\begin{figure}[]
  \centering
  \includegraphics[width = 0.35\textwidth]{modelGraph/modelGraphNoMath.pdf}
  \caption{The data-generating model as a probabilistic graphical model, following conventions
    of \citet{LeeWagenmakers2013:Bayesian-Cognit}. Shaded nodes are observed, white nodes are
    latent variables. Square nodes represent categorical, round nodes continuous
    variables. Boxes indicate scope of indices.}
  \label{fig:ModelGraph}
\end{figure}

@@

Means and bounds of 95\% HDIs of the posteriors for model parameters are in
Table~\ref{tab:SummaryStats}. Posterior credible levels of $w$ allow for a limited amount of
slack around $Q_j$. Values for $\kappa$ indicate that, on average, participants had no
preference for or against extreme slider ratings. Relatively high values of $a$ indicate that
participants, on average, had a strong tendency to choose modal in the \emph{give-a-number}
task.
\begin{table}[ht]
\centering
\footnotesize
\begin{tabular}{rlllll}
 & $w$ & $\kappa$ & $\sigma$ & $a$ & $b$ \\ \midrule
  lower & 14.65 &  0.98 &  0.26 & 22.04 &  1.11 \\ 
  mean & 15.55 &  0.99 &  0.28 & 27.43 &  1.27 \\ 
  upper & 16.48 &  0.99 &  0.31 & 32.95 &  1.42 \\ 
\end{tabular}
\caption{Summary statistics for posteriors on parameters}
\label{tab:SummaryStats}
\end{table}

Of most theoretical interest are posterior estimates of $Q_j$. \figref{fig:PosteriorQj} shows
means of the posterior $Q_j$s, with their 95\% HDIs, alongside the mean slider ratings. The
latter provide a very good approximation of the latent, inferred population-level
beliefs. Inspection of posteriors of individual $P_{ij}$ shows that there is ample variation
between participants. Nonetheless, the way the model suggests we should think about harnessing
the individual $P_{ij}$s under a population-level central tendency is closely approximated by
mean slider ratings. Although the match is not perfect, it is good enough to say that the
latter are a practical way of approximating what the crowd believes despite individual
differences.

\begin{figure}
  \centering
  \includegraphics[width = 0.5\textwidth]{plots/pop_priors.pdf}
  \caption{Means of posteriors over $Q_j$ in black with gray area indicating 95\% HDIs. Red: mean slider ratings.}
  \label{fig:PosteriorQj}
\end{figure}

@@

MF's work was supported by the Institutional Strategy of the University of T̈\"{u}bingen
(DFG, ZUK 63). MF, FD, AS and JD's work was supported by the
Priority Program XPrag.de (DFG Schwerpunktprogramm 1727). This work was further supported by
ONR grant N00014-13-1-0788 and a James S. McDonnell Foundation Scholar Award to NDG and an SNF
Early Postdoc.Mobility Award to JD.
